An analysis of interrelations between economic and environmental variables in Australian Winegrowing.

### 2023-10-15 article.tex
backing up prior changes

@@

\begin{figure}
 \resizebox{\textwidth}{!}{
 \includegraphics{operating_costs.png}}
 % FIXME: What are the #'s? What do the sizes mean? What are the colours? What is interrelated importance?
 % FIXME: Mark one Panel A and the other B
 \caption{The left-hand side depicts the 10 most important variables in predicting Operating Costs using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:operating_costs_sankey}
\end{figure}

>>>>

Operating cost

@@

\begin{figure}
 \resizebox{\textwidth}{!}{
 \includegraphics{operating_costs.png}}
 % FIXME: Mark one Panel A and the other B This still needs to be done in the actual pictures
 \caption{The left-hand side, A,  depicts the 10 most important variables in predicting Operating Costs using XGBoosted trees as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:operating_costs_sankey}
\end{figure}
